\documentclass[12pt]{article}
\textheight=9in
\textwidth=6.5in
\topmargin=-.5in
\evensidemargin=0in
\oddsidemargin=0in
\begin{document}
\begin{center}
{\Large\bf Scoreboard Software}
\end{center}

\section{Introduction}

This is for use in any contest where player VM services are monitored and
scored.  An administrator adds players and their associated ip addresses to a
data base. The scoring is started by the administrator after the database is
complete.  Probing of services commenses and each VM is probed every 20
seconds but this can be changed.  For each service that is considered 'up'
as a result of a probe the player gets one point but this can be changed.
Players may be added or deleted after scoring begins.  Probing of an added 
player begins immediately.  Probing of a deleted player ends.  Scoring is saved
in a player's database file which is named players.db but this name can be
changed.  A utility exists to read the player's database file.  Another utility
exists to create a webpage showing scores and rankings from the player's
database file.  This is intended to be run on a computer's command shell.  Some
modifications to the scripts are necessary for Windows computers.

\section{Before Scoring Begins}

From the command line run
\begin{verbatim}
   cdx-interactive.run
\end{verbatim}
If there is no player's database file a warning is issued.  In any case a prompt
appears like this:
\begin{verbatim}
   Command>
\end{verbatim}
To add a player to the database run the {\tt AddPlayer} command with the
player's name and IP address as arguments. For example, like this:
\begin{verbatim}
   Command> AddPlayer Jonas 192.168.1.1
\end{verbatim}
At the command prompt show all the players with their current scores and IP
addresses using {\tt ListPlayers}.  For example:
\begin{verbatim}
   Command> ListPlayers 
   player: Jonas   192.168.1.1   0
   player: Jake    192.168.1.2   0
\end{verbatim}
At the command prompt save the current database in the player's database file
using {\tt SavePlayers}.  For example:
\begin{verbatim}
   Command> SavePlayers
\end{verbatim}
A saved database file can be loaded using {\tt LoadPlayers} like this:
\begin{verbatim}
   Command> LoadPlayers
\end{verbatim}
Players can also be deleted from the database at any time (while scoring or not)
using {\tt DeletePlayer} like this where only the player's name need be given as
an argument:
\begin{verbatim}
   Command> DeletePlayer Jonas
\end{verbatim}

\section{Scoring}

Scoring begins when invoking the {\tt Start} command like this:
\begin{verbatim}
   Command> Start
\end{verbatim}
Scoring proceeds as follows.  A while loop contains a for loop which starts a
{\tt CheckServices} thread for each player in the contest followed by a delay
that is determined by a value in a {\tt GameParameters} file (more about this
later).  The default value is 2 seconds.  Each {\tt CheckServices} thread 

\end{document}
